Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-30 edubots_surveys.Rnw

Responses were stored automatically in a Google Drive spreadsheet. Eventually,
the results from the two forms we used for the first survey were collated in a
single spreadsheet. Next, we show the results and analyse them.

>>>>

Responses were stored automatically in a Google Drive spreadsheet. Eventually,
the results from the two forms we used for the first survey were collated in a
single spreadsheet.

\textcolor{blue}{The second survey was designed after initial results to the first survey arrived,
and pointed to necessities and experiences of teachers not being addressed by the first one; namely
their experience with messaging platforms and the way they were used to interact with students.
It was piloted in a group of university teachers attending to a formation course, and validated with them.
It was then extended to the rest of the responders, using the same media: Telegram groups, email and
and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
(Section \ref{app:questions}).}

Next, we show the results and analyse them.
